Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-08-06 tex/MesnardoBarba2019.tex
Add description about Singularity containers

Command-line utilities such as Azure CLI and Batch Shipyard were of great help to create and manage resources on Microsoft Azure for executing our reproducible research workflow.
(In our lab, we tend to avoid interacting directly with graphical-user interfaces to keep a trace of the commands run and make the workflow more reproducible.)
Azure CLI helped us set up the Azure Batch and Storage accounts as well as moving data between the cloud platform and our local machines.
Thanks to Batch Shipyard, we did not have to dig into the software development kit of Azure Batch to use the service.
Writing YAML configuration files was all we needed to do to create a pool of virtual machines with Batch Shipyard and to submit jobs to it.
With Batch Shipyard, we have painlessly submitted jobs on Azure Batch to run multi-instance tasks in Docker containers, everything from the command-line terminal on a local machine.
Note that Batch Shipyard also supports Singularity containers.

>>>>

Command-line utilities such as Azure CLI and Batch Shipyard were of great help to create and manage resources on Microsoft Azure for executing our reproducible research workflow.
(In our lab, we tend to avoid interacting directly with graphical-user interfaces to keep a trace of the commands run and make the workflow more reproducible.)
Azure CLI helped us set up the Azure Batch and Storage accounts as well as moving data between the cloud platform and our local machines.
Thanks to Batch Shipyard, we did not have to dig into the software development kit of Azure Batch to use the service.
Writing YAML configuration files was all we needed to do to create a pool of virtual machines with Batch Shipyard and to submit jobs to it.
With Batch Shipyard, we have painlessly submitted jobs on Azure Batch to run multi-instance tasks in Docker containers, everything from the command-line terminal on a local machine.
Note that Batch Shipyard also supports Singularity containers.
Singularity is an open source container platform designed for HPC workloads.
Singularity containers can be used on traditional HPC clusters such as Colonial One; Docker containers usually cannot.
Indeed, running a Docker container involves running a Docker daemon (a background process) which requires root privileges (that users do not and should not have on production clusters).
The container technology from Singularity was designed from the ground up to prevent escalation in user privileges.
